---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

```{r, include = FALSE}
  knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    fig.path = "man/figures/README-",
    out.width = "100%"
)
```

# VOX (verbal operant experimental) Analysis 

*NOTE: THIS PACKAGE IS IN DEVELOPMENT. USE AT YOUR OWN DISCRETION*

The `{voxanalysis}` package provides a framework for diagnosing autism spectrum disorder It contains both the VOX Analysis Application (see below) and individual functions for measurements and data visualizations.

![Placeholder Image](https://via.placeholder.com/150)

## Background

The `{voxanalysis}` package is meant to provide easily generated reports and analysis using the VOX Analysis framework.

It was developed by Dr. Lee Mason and Dr. Alonzo Andrews, two researchers in verbal behavior and founders of Shapers at Work, a consulting firm that teaches behavioral specialists about autism diagnosis.

People with autism tend to have more variation with respect to language development. 

For example, they may be good at requesting something, but not at responding to a question. A person without autism will have a balanced set of language skills, which means their ability to request something is nearly the same as their ability to respond to a question.

VOX Analysis involves an in-person evaluation (i.e., play therapy), where the listener (e.g., a behavioral analyst or clinician) elicits a response from the speaker (i.e., the patient). (Read more on this process here.)

Once the listener has recorded the responses, they can use the `{voxanalysis}` package to run a generate data visualizations and measures of variance.

## Installation

A user can install `{voxanalysis}` with:

```{r, eval = FALSE}
# If devtools is not installed, first install it
install.packages("devtools")

# Install PackageName from GitHub
devtools::install_github("Free-State-Analytics/voxanalysis")
```

## Running Reports

The easiest way to generate a report is through the VOX Analysis Application. 

This Shiny application can run with:

```{r, eval = FALSE}
voxanalysis::run_app()
```

A user with R programming experience can generate a MS Word version of the report too.

Read [How to Generate Reports](https://free-state-analytics.github.io/voxanalysis/articles/generatingreports.html) to learn more about report generation.

## Individual Calculations and Data Visualizations

Users with more R programming experience can use individual components from the VOX Analysis Application. All data visualizations and measures are including in the `{voxanalysis}` package.

Read [VOX Visualizations and Metrics](https://free-state-analytics.github.io/voxanalysis/articles/datavizandcharts.html)  to learn more about these functions.

A user with R programming experience can generate individual data visualizations and a MS Word version of the report too.

## About the Team

The `{voxanalysis}` package was developed by Lee Mason, Alonzo Andrews, and Taylor Rodgers. 

### Dr. Lee Mason
*Coming soon*

### Dr. Alonzo Andrews
*Coming soon*

### Taylor Rodgers
*Coming soon*

## Services Offered

*Coming soon*

