---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
  knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    fig.path = "man/figures/README-",
    out.width = "100%"
)
```

# VOX Analysis

*NOTE: THIS PACKAGE IS IN DEVELOPMENT MANY KEY MEASURES AND DATA VISUALIZATIONS HAVE NOT BEEN TESTED OR VERIFIED YET.*

`voxanalysis` is an R package and R Shiny application for autism spectrum diagnosis. It provides a user-interface that allows for user inputs following the VOX Analysis evaluation process defined here. Its data visualization functions are also available for analysts to use for custom requirements.

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

## Installation

You can install the development version of `{voxanalysis}` like so:

```{r, eval = FALSE}
# If devtools is not installed, first install it
install.packages("devtools")

# Install PackageName from GitHub
devtools::install_github("Free-State-Analytics/voxanalysis")

```

## Run

You can launch the application by running:

```{r, eval = FALSE}
voxanalysis::run_app()
```

## About

You are reading the doc about version : `r golem::pkg_version()`.

This README has been compiled on `r Sys.time()`.

Here are the tests results and package coverage:

```{r, error = TRUE}
devtools::check(quiet = TRUE)
```

```{r echo = FALSE}
unloadNamespace("voxanalysis")
```

```{r, error = TRUE}
covr::package_coverage()
```
