---
title: "VOX Visualizations and Metrics"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{VOX Visualizations and Metrics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```

```{r setup, echo = FALSE}
library(voxanalysis)
library(cowplot)
library(dplyr)
library(tidyr)
library(kableExtra)
library(ggplot2)
data(df_input_response_example)

df_autism <- df_input_response_example
df_wo_autism <- df_input_response_example
df_wo_autism <- df_input_response_example
df_wo_autism$conversing <- c(1, 1, 1, 0, 1, 1)
df_wo_autism$requesting <- c(1, 1, 1, 0, 1, 1)

```

*Note: This page is in the process of being written. Some sections may be incomplete. Apologies for any confusion. We expect this page to be finished in the next two weeks.*

### Introduction

The VOX Analysis Application and Package provide many distinct data visualizations and measures of variability to assist a user in diagnosing a speaker with autism spectrum disorder.

This article provides descriptions for these various measures, data visualizations, and tables found in the reports. It also provides (as an extra resource) instructions for R users to produce these resources using the `{voxanalysis} package, without needing to access the application.

A user can generate a summary report with these measures, data visualizations, and tables with the instructions found [here](./generatingreports.html).

<br>
<br>

### Optional: Use `{voxanalysis}` Package

Though the VOX Application is the recommended way for most users to generate reports, R users can generate the same statistical measures, data visualizations, and tables found in the report using the `{voxanalysis}` package directly. Psychometricians and researchers may find this approach more preferable.

The package's R functions use the following prefixes:

 - **calc_** functions return a vector or list with the measure(s) of interest
 
 - **plot_** functions return a data visualization
 
 - **table_** functions return a data.frame

<br>
<br>

### Area Q Plot

The Area Q plot shows a visual representation of the speaker's verbal repertoire, illustrating the balance (or lack thereof) across the four [response types](https://free-state-analytics.github.io/voxanalysis/articles/datadefinitions.html#response-type) (conversing, labeling, echoing, and requesting).

The two Area Q plots below show two different speakers. The one on the left shows a speaker with a verbal repertoire more typical of a person with autism, because there is an imbalance between the four response types. The labeling and echoing of the speaker with autism is disproportionately strong compared to conversing and requesting. The speaker on the right shows relative balance in all four response types, which is tyipcial of someone without autism.

<br>

```{r, echo = FALSE}

df_summarized_austim <- util_summarize_response(df_autism)
df_summarized_wo_austim <- util_summarize_response(df_wo_autism)

plot_grid(
  plot_area_q(
    df_summarized_response = df_summarized_austim,
    ind_doc_version = FALSE    
  ),
  plot_area_q(
    df_summarized_response = util_summarize_response(df_wo_autism),
    ind_doc_version = FALSE    
  ),
  labels = c("With Autism", "Without Autism")
)
```

<br>

An R user can generate Area Q Chart using the `plot_area_q` function. 

The function requires a parameter called `df_summarized_response` that follows the [Summary Data](https://free-state-analytics.github.io/voxanalysis/articles/datamodel.html#summarizedata) data model. An example of this data frame can be seen with `data("df_summarized_response_example")`. 

Note that this function can accept only two distinct `date_of_evalution` entry inside `df_summarized_response`. The user will need to set the `date_primary` parameter in `plot_area_q` to a specific `date_of_evaluation` if there are more than two unique `date_of_evaluation`.

See `?plot_area_q` and `?df_summarized_response_example` for more details.

<br>

```{r, eval = FALSE}
library(dplyr)
data("df_summarized_response_example")

df_summarized_response <- df_summarized_response_example %>%
  slice_max(order_by = date_of_evaluation, n = 2)

plot_area_q(
  df_summarized_response, 
  date_primary = max(df_summarized_response$date_of_evaluation) # use date_primary to determine darker color on plot
  )
```

<br>

```{r, echo = FALSE}
library(dplyr)
data("df_summarized_response_example")

df_summarized_response <- df_summarized_response_example %>%
  slice_max(order_by = date_of_evaluation, n = 2)

plot_area_q(
  df_summarized_response, 
  date_primary = max(df_summarized_response$date_of_evaluation) # use date_primary to determine darker color on plot
  )
```

<br>
<br>

### Area Q Metrics

The Area Q plot can be supplemented by additional metrics:

1. **Centroid** is the geometric center of all four points drawn by the plot
2. **Centroidal Distance** is the distant of the centroid from the chart's origin (0, 0)
3. **Moment of Area Q** is the area of the polygon displayed on the chart

The results for these calculations vary based on whether a speaker has autism. 

A centroidal distance closer to 0 is typical of person without autism, whereas a centroidal distance further from 0 indicates greater disproportionality their verbal repertoire. If the VOX Analysis contains 12 referents, the maximum centroidal distance possible is 6, which indicates a far higher chance that the speaker has autism.

Moment of Area Q represents the size of the speaker's language repertoire, as shown on the Area Q plot. A larger number is more typical of a person without autism, while a smaller number is more typical of a speaker with autism.

<br>

```{r, echo = FALSE}
data("df_input_response_example")
l_centroid_autism <- calc_centroid(df_autism)
l_centroid_wo_autism <- calc_centroid(df_wo_autism)
l_centroid_autism$centroid <- paste0("( x = ", l_centroid_autism$centroid[1], ", y = ", l_centroid_autism$centroid[2],")")
l_centroid_wo_autism$centroid <- paste0("( x = ", l_centroid_wo_autism$centroid[1], ", y =", l_centroid_wo_autism$centroid[2],")")

rbind(
  l_centroid_autism %>% as.data.frame() %>% mutate(distance = as.character(distance), moment = as.character(moment), type = "With Autism"),
  l_centroid_wo_autism %>% as.data.frame() %>% mutate(distance = as.character(distance), moment = as.character(moment), type = "Without Autism")
) %>%
  pivot_longer(cols = c(centroid, distance, moment)) %>%
  pivot_wider(id_cols = name, names_from = type, values_from = value) %>%
  rename(Measure = name) %>% 
  kableExtra::kable() %>%
  kable_styling(position = "center")

```

<br>

An R user can generate the Area Q Metrics using the `calc_centroid` function. 

The function requires a parameter called `df_input_response` that follows the [Speaker Data](https://free-state-analytics.github.io/voxanalysis/articles/datamodel.html#speakerdata) data model. An example of this data frame can be seen with `data("df_input_response_example")`. 

Note that this function can accept only one distinct `date_of_evalution` entry inside the `df_input_response`. 

See `?calc_centroid` and `?df_input_response_example` for more details.

<br>

```{r, eval = FALSE}
data("df_input_response_example")
calc_centroid(df_input_response = df_input_response_example)
```

<br>
<br>

### VOX Line Chart

The VOX line chart shows the response types over verbal episodes. Since each verbal episode attempts to solicit a particular response from the speaker, this tells the clinician or behavioral analyst how those response vary over the session.

The two VOX line charts below show two speakers. The speaker on the left is more typical of a person with autism. There is more dispersion in their response types, which continues across all verbal episodes. The speaker on the right is more typical of a person without autism. There is more clustering and overlapping of the lines, indicating more variability *within* a response type, as opposed to variability *between* response types.

<br>

```{r, echo = FALSE}
plot_grid(
  plot_vox_line(
    df_autism,
    ind_hide_heading = TRUE,
    ind_doc_version = TRUE
  ) +
    theme(legend.position = "bottom")
  ,
  # + theme(#plot.margin = margin(t = 60, r = 30, l = 30, b= 30),
  #           legend.position = "bottom",
  #           legend.text = element_text(size = 8)),
  plot_vox_line(
    df_wo_autism,
    ind_hide_heading = TRUE,
    ind_doc_version = TRUE
  ) + theme(plot.margin = margin(t = 50, r = 30, l = 30, b = 30+ 42.25),
            legend.position = "none"),
  labels = c("With Autism", "Without Autism")
)

```

<br>

An R user can generate the VOX Line Chart using the `plot_vox_line` function. 

The function requires a parameter called `df_input_response` that follows the [Speaker Data](https://free-state-analytics.github.io/voxanalysis/articles/datamodel.html#speakerdata) data model. An example of this data frame can be seen with `data("df_input_response_example")`. 

Note that this function can accept only one distinct `date_of_evalution` entry inside the `df_input_response`. 

See `?plot_vox_line` and `?df_input_response_example` for more details.

<br>

```{r, eval = FALSE}
# Load example data
data("df_input_response_example")

# Generate a VOX line chart across verbal episodes
plot_vox_line(
  df_input_response = df_input_response_example,
  ind_hide_heading = FALSE)
```

<br>

```{r, echo = FALSE}
# Load example data
data("df_input_response_example")

# Generate a VOX line chart across verbal episodes
plot_vox_line(
  df_input_response = df_input_response_example,
  ind_hide_heading = FALSE,
  ind_doc_version = TRUE)
```

<br>
<br>

### VOX Pie Chart

The VOX Pie Chart shows a visual representation of the speaker's verbal repertoire, illustrating the balance (or lack thereof) across the four [response types](https://free-state-analytics.github.io/voxanalysis/articles/datadefinitions.html#response-type) (conversing, labeling, echoing, and requesting). The pie chart is similar to the Area Q plot, although it is easier for lay people to understand and uses a different set of metrics.

The two VOX Pie Charts below show two different speakers. The speaker on the left is more typical of a person with autism. The labeling and echoing of the speaker with autism is disproportionately strong compared to conversing and requesting. The speaker on the right shows relative balance in all four response types, which is more typical of someone without autism.

<br>

```{r, echo = FALSE}

df_summarized_austim <- util_summarize_response(df_autism)
df_summarized_wo_austim <- util_summarize_response(df_wo_autism)

plot_grid(
  plot_vox_piechart(
    df_summarized_austim,
  ),
  plot_vox_piechart(
    df_summarized_wo_austim,
  ),
  labels = c("With Autism", "Without Autism")
)
```

<br>

An R user can generate VOX Piechart using the `plot_vox_piechart` function. 

The function requires a parameter called `df_summarized_response` that follows the [Summary Data](https://free-state-analytics.github.io/voxanalysis/articles/datamodel.html#summarizedata) data model. An example of this data frame can be seen with `data("df_summarized_response_example")`. 

Note that this function can accept only one distinct `date_of_evalution` entry inside the `df_summarized_response`. 

See `?plot_vox_piechart` and `?df_summarized_response_example` for more details.

<br>

```{r, eval = FALSE}
# Load and transform df_input_response_example
data("df_input_response_example")
df_summarized_response <- util_summarize_response(df_input_response_example)

### Alternatively
# data("df_summarized_response_example")
# df_summarized_response <- udf_summarized_response_example

# Generate the VOX pie chart
plot_vox_piechart(
  df_summarized_response = df_summarized_response)
```

<br>

```{r, echo = FALSE, message = FALSE, warning = FALSE}
# Load and transform df_input_response_example
data("df_input_response_example")
df_summarized_response <- util_summarize_response(df_input_response_example)

### Alternatively
# data("df_summarized_response_example")
# df_summarized_response <- df_summarized_response_example

# Generate the VOX pie chart
plot_vox_piechart(
  df_summarized_response = df_summarized_response)
```

<br>
<br>

### Speaker's SCoRE

The Speaker's SCoRE, which stands for *Speech Coefficient of Reliability and Engagement*, quantifies the findings of the VOX Pie Chart to indicate balance or imbalance. The measure provides a range from 0 to 1, with 0 being functionally non-verbal and 1 representing a fluent verbal repertoire.

There are two Speaker's SCoREs show below. The SCoRE on the left is more typical of a person with autism. The SCoRE on the right is more typical of a person without autism and verbally fluent.

<br>

```{r, echo = FALSE, message = FALSE, warning = FALSE}
df_summarized_austim <- util_summarize_response(df_autism)
df_summarized_wo_austim <- util_summarize_response(df_wo_autism)

data.frame(
  "With Autism" = calc_speakers_SCoRE(df_summarized_response = df_summarized_austim),
  "Without Autism" = calc_speakers_SCoRE(df_summarized_response = df_summarized_wo_austim)
) %>% 
  kableExtra::kable(col.names = c("With Autism", "Without Autism")) %>%
  kable_styling(position = "center")

```

<br>

Down below is a guide of Speaker's SCoREs and how they can help a behavioral analyst with diagnosis.

<br>

```{r, echo = FALSE} 

data.frame(
  SCoRE = c("0 to .19", ".20 to .49", ".50 to .79", ".80 to 1.00"),
  Intepretation = c("Emergent", "Pratical", "Moderate", "Strong")
) %>% 
  kableExtra::kable() %>%
  kable_styling(position = "center")

```

<br>

An R user can generate Speaker's SCoRE using the `calc_speakers_score` function. 

The function requires a parameter called `df_summarized_response` that follows the [Summary Data](https://free-state-analytics.github.io/voxanalysis/articles/datamodel.html#summarizedata) data model. An example of this data frame can be seen with `data("df_summarized_response_example")`. Note that this function can accept only one distinct `date_of_evalution` entry inside the `df_summarized_response`. 

See `?calc_speakers_score` and `?df_summarized_response_example` for more details.

<br>

```{r, eval = FALSE}

# Load and transform df_input_response_example
data("df_input_response_example")
df_summarized_response <- util_summarize_response(df_input_response_example)

### Alternatively
# data("df_summarized_response_example")
# df_summarized_response <- df_summarized_response_example

# Calculate the Speaker's SCoRE
calc_speakers_SCoRE(df_summarized_response = df_summarized_response)
```

<br>
<br>

### Cochran's Q Test Table

Cochran's Q Test looks at the natural variability 

Down below are Cochran's Q Test metrics for a speaker with autism and a speaker without autism.

<br>

```{r, echo = FALSE, message = FALSE, warning = FALSE} 

df_coch_autism <- table_cochrans_q_test(df_input_response = df_autism)
df_coch_wo_autism <- table_cochrans_q_test(df_input_response = df_wo_autism)

df_coch_autism %>%
  rename("With Autism" = value) %>%
  inner_join(df_coch_wo_autism, by = c("label" = "label")) %>%
  mutate(value = round(value, 4)) %>%
  rename("Measure" = label, "Without Autism" = value) %>%
  kableExtra::kable()  %>%
  kable_styling(position = "center")

```

<br>

An R user can generate the Cochran's Q Test using the `table_cochrans_q_test` function. 

The function requires a parameter called `df_input_response` that follows the [Speaker Data](https://free-state-analytics.github.io/voxanalysis/articles/datamodel.html#speakerdata) data model. An example of this data frame can be seen with `data("df_input_response_example")`. Note that this function can accept only one distinct `date_of_evalution` entry inside the `df_input_response`. 

See `?table_cochrans_q_test` and `?df_input_response_example` for more details.

<br>

```{r, eval = FALSE}
# Load example response data
data("df_input_response_example")

# Generate a summary table with Cochran's Q test and supporting statistics
table_cochrans_q_test(df_input_response = df_input_response_example)
```

<br>
<br>

### Hierarchy Table

The Hierarchy Table is...

The table below shows a speaker with autism. The clinician would start an intervention by focusing on...

<br>

```{r, echo = FALSE}
data("df_summarized_response_example")

# Filter to a single evaluation date, as the table works with one date at a time
dat <- df_summarized_response_example %>%
    filter(date_of_evaluation == max(date_of_evaluation))

# Generate the prompt hierarchy table
table_prompt_hierarchy(df_summarized_response = dat) %>%
  kableExtra::kable() %>%
  kable_styling(position = "center")
```

<br>

An R user can generate the Prompt Hierarchy using the `table_prompt_hieararchy` function. 

The function requires a parameter called `df_summarized_response` that follows the [Summary Data](https://free-state-analytics.github.io/voxanalysis/articles/datamodel.html#summarizedata) data model. An example of this data frame can be seen with `data("df_summarized_response_example")`. 

Note that this function can accept only one distinct `date_of_evalution` entry inside the `df_summarized_response`. 

See `?table_prompt_hieararchy`, `?df_summarized_response_example`, and `?util_summarize_response` for more details.

<br>

```{r, eval = FALSE}
# Load example data
library(dplyr)
data("df_summarized_response_example")

# Filter to a single evaluation date, as the table works with one date at a time
dat <- df_summarized_response_example %>%
    filter(date_of_evaluation == max(date_of_evaluation))

# Generate the prompt hierarchy table
table_prompt_hierarchy(df_summarized_response = dat)
```

<br>
<br>
<br>
<br>
