---
title: "How to Generate Word Doc Report"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{How to Generate Reports}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(voxanalysis)
```

If the user knows how to use R and has downloaded the `voxanalysis` pacakge, they can use the function below to generate a Word Doc report. See `?util_generate_word_doc_report` for more information.

```{r, eval = FALSE}
# Load example data sets
data("df_input_speaker_info_example")
data("df_input_response_example")

# Generate a Word document report
util_generate_word_doc_report(
  df_input_speaker_info = df_input_speaker_info_example,
  df_input_response = df_input_response_example,
  file_name = "test.docx"
)

```

Note that using `util_generate_word_doc_report` can be tedious when it comes to data management. A user must follow the [data model](https://free-state-analytics.github.io/voxanalysis/articles/datamodel.html) exactly, otherwise the Word Doc will not generate.
