---
title: "How to Generate Reports"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{How to Generate Reports}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(voxanalysis)
```

The `voxanalysis` package provides the user two ways to generate a report:

* The R Shiny application
* Word Doc generation

The user can also generate individual data visualizations and measures of variability using the functions defined [here](./datavizandcharts.html).

## Word Doc Report

If the user knows how to use R and has downloaded the `voxanalysis` pacakge, they can use the function below to generate a Word Doc report. See `?util_generate_word_doc_report` for more information.

```{r, eval = FALSE}
# Load example data sets
data("df_input_speaker_info_example")
data("df_input_response_example")

# Generate a Word document report
util_generate_word_doc_report(
  df_input_speaker_info = df_input_speaker_info_example,
  df_input_response = df_input_response_example,
  file_name = "test.docx"
)

```


Note that using `util_generate_word_doc_report` can be tedious when it comes to data management. A user must follow the [data model](https://free-state-analytics.github.io/voxanalysis/articles/datamodel.html) exactly, otherwise the Word Doc will not generate.

## R Shiny Application

The R Shiny Application is the recommended way for generating a report, appending data, etc.

To launch the application, simply run: `voxanalysis::run_app()`.

We'll go into more steps below.

## R Shiny Prompts

A guide to various prompts that appear in the R Shiny application.

### Select Data Upload Method

The first menu let's you decide how to enter data.

Selecting **Type in new data** means you will manually type both the speaker info and then the responses from the evaluation.

Selecting **Upload a .csv file** if you want to re-run a report with previously exported data. Alternatively, you can also use this path if you find it easier to record your data to a .csv file beforehand, rather than use the application to hand type data. You'll also have the opportunity to modify the speaker data that accompanies it.

Select **Both** is useful when you have a previous data set that you want to append new response data.

### Provide Speaker Info

The **Provide Speaker Info** prompt is asking for the speaker's information, such as first name, last name, birth date, and evaluation date. Language spoken and gender are optional entries to include as well.
 
The speaker information will be fed into any Word Doc or .csv exports.

### Upload Data Set

The **Upload Data Set** prompt appears when the user indicated they wanted to upload a data set. This data set is usually one that the user previously exported from the **Results Summary** page. Exporting a data set from the Results Summary page ensures the data is structured in a way that it can be re-uploaded, re-analyzed, or appended in the future.

However, a user may also upload a new data set, provided it follows the data model [guidelines](https://free-state-analytics.github.io/voxanalysis/articles/datamodel.html).

Once the user has uploaded a .csv file, they will have the option to modify the speaker info.

If the user did not previous select the option to add new data, they can select **Download Report** for a Word Doc or select **Show Report** to see the report within the web application. Otherwise, they can hit **Continue** to move onto the **Provide Speaker Responses** prompt.

### Provide Speaker Responses

The **Provide Speaker Responses** prompt asks the user for the number of referents (i.e., toys) used in the evaluation. This will change the number of rows found in the input table below.

The user will then need to provide unique referent names and the responses (1 = Positive Response, 0 = No Response) to those referents based on the verbal oeprant (CLEaR).

### Results Summary Page

The **Results Summary Page** provides the VOX Analysis results for the speakers responses the user provided. 

The user will have the option to **Download Report** to download a Word Doc version, or they can select **Save Data**, which allows them to download the data set they had previously entered.
