---
title: ""
format: docx
params:
  df_input_speaker_info: NA
  df_input_response: NA
  df_summarized_response: NA
execute:
  echo: FALSE 
  warning: FALSE
  error: FALSE
---

```{r results='asis'}
library(voxanalysis)
library(dplyr)
library(flextable)
### quarto_render changes date fields to a numeric value. This explicitly returns them to a date value.
df_input_response <- params$df_input_response %>% 
  as.data.frame() %>%
  mutate(date_of_evaluation = as.Date(date_of_evaluation, origin = "1970-01-01"))
df_summarized_response <- params$df_summarized_response %>% 
  as.data.frame() %>%
  mutate(date_of_evaluation = as.Date(date_of_evaluation, origin = "1970-01-01"))
speaker_full_name <- paste0(params$df_input_speaker_info$first_name, " ", params$df_input_speaker_info$last_name)
centroids <- calc_centroid(df_input_response)
```

### `r speaker_full_name`'s VOX Analysis

*Evaluation date: `r as.Date(max(params$df_input_response$date_of_evaluation), origin = "1970-01-01")`*

The VOX analysis (*verbal operant experimental*) evaluates the language repertoire for `r speaker_full_name`, in order to provide an accurate autism spectrum disorder diagnosis.

A balanced repertoire implies that the speaker has a normal language development. An imbalance, measured and visualized below, implies the speaker has autism spectrum disorder.

### Clinician's Conclusions / Recommendations

***Please provide any supplemental information or conclusions here. Otherwise, you can delete this section***

### Responses

During a session, `r speaker_full_name` was supplied with several referants to interact with (i.e., toys and other objects). The listener engaged with `r speaker_full_name` to solicit a positive response to a verbal operant (conversing, listening, echoing, and repeating).

The table below shows the way `r speaker_full_name` responded:

```{r}

if (length(unique(df_input_response$date_of_evaluation)) > 1) {
  data_to_pass <- df_input_response %>% 
    rename(`Evaluation Date` = "date_of_evaluation",
           `Referent Order`  = "referent_order",
           Referent = "referent",
           Conversing = "conversing",
           Labeling = "labeling",
           Echoing = "echoing",
           Requesting = "requesting")
} else {
  data_to_pass <- df_input_response %>% 
    select(-"date_of_evaluation") %>% 
    rename(Referent = "referent",
           `Referent Order`  = "referent_order",
           Conversing = "conversing",
           Labeling = "labeling",
           Echoing = "echoing",
           Requesting = "requesting")
}

flextable(data_to_pass, cwidth =1.1) %>%
  theme_zebra()

```

### Area Q Plot

The Area Q plot helps visualize variance. A speaker with normal language development will have roughly equal points on each axis. A speaker with abnormal language development will have unequal points on each axis.

-   Centroid: **`r paste0("(",centroids$centroid[1],", ",centroids$centroid[2],")")`**

-   Centroidal distance: **`r centroids$distance`**

-   First moment of area Q: **`r centroids$moment`**


```{r}
#| fig-height: 3
#| fig-width: 3
#| fig-align: center
plot_area_q(
  df_summarized_response = df_summarized_response,
  date_primary = max(df_summarized_response$date_of_evaluation),
  ind_doc_version = TRUE)
```

### VOX Chart

The VOX Chart shows the responses based on the verbal episode. A speaker with normal language development will have relatively straight lines that overlap one another most of the time.

```{r}
#| fig-height: 2.5
#| fig-align: center
plot_vox_line(
  df_input_response = df_input_response,
  ind_hide_heading = FALSE,
  ind_doc_version = TRUE)
```

### Cochran's Q

Cochran's Q is a statistical test is used to verify whether the speaker has a balanced repertoire. A p-value less than 0.05 means we reject the null in favor of the alternative that the speaker does have an imbalance.

```{r}
flextable(
  table_cochrans_q_test(
    df_input_response = df_input_response %>%
      filter(.data$date_of_evaluation == max(.data$date_of_evaluation))
    )
  , cwidth = 1.5
) %>%
  delete_part(part = "header") %>%
  theme_zebra()
```

### SCoRE

The speaker has a SCoRE of **`r calc_speakers_SCoRE(df_summarized_response = df_summarized_response)`**.

*Stimulus Control Ratio Equation (SCoRE)* measures the proportionality of the speaker's repertoire on a scale of 0 to 1. A higher number indicates balanced language assessment.

The pie chart below further illustrates this balance or imbalance.

```{r}
#| fig-height: 2.5
#| fig-width: 2.5
#| fig-align: center
plot_vox_piechart(
  df_summarized_response = df_summarized_response %>%
    filter(.data$date_of_evaluation == max(.data$date_of_evaluation)),
  ind_doc_version = TRUE
)
```

### Prompt Hierarchy

```{r}
flextable(
  table_prompt_hierarchy(
    df_summarized_response = df_summarized_response %>%
      filter(.data$date_of_evaluation == max(.data$date_of_evaluation))
  ),
  cwidth = 1.1
) %>%
  theme_zebra()
```

